Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
Slight adjustments to carbonate budget methods and results

The relationship between the number of years above $\beta_{0}$ and median reef depth was
then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
adopted as reef depth distributions are expected to be non-normal and highly skewed.
Furthermore, reefs are naturally of different types and experience different conditions,
and so the monotonic trends (whether the relationship consistently increase or decrease)
rather than the exact quantative relationship is of interest.

@@

Reefs with greater median depth levels maintain coral cover above
indicative carbonate budget levels for a longer time frame compared to reefs with shallower
median depths [@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate
positive correlation with the number of years a reef maintains coral cover above the
required threshold [@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget
maintainence correlation decreases as the required carbonate budget threshold increases.
This is likely due to an increasing number of reefs being unable to maintain coral cover
above threshold levels as the threshold increases. There are no clear relationships between
reef total connectivity levels and the number of years reefs maintain coral cover above
carbonate budget threshold levels [@sfig-access-esm1-5-conn-carbonate]. The natural log of
total connectivity strength was found to have no correlation with the number of years a reef
maintains cover above the required thresholds. Log connectivity strength - carbonate budget
maintainence correlation slightly decreases as the required carbonate budget threshold
increases.

>>>>

The relationship between the number of years above $\beta_{0}$ and median reef depth was
then assessed with Spearman's rank correlation. Spearman's correlation coefficient was
adopted as reef depth and connectivity strength distributions are expected to be non-normal and
highly skewed. Furthermore, reefs are naturally of different types and experience different 
conditions, and so the monotonic trends (whether the relationship consistently increase or 
decrease) rather than the exact quantative relationship is of interest.

@@

Reefs with greater median depth levels maintain coral cover above
indicative carbonate budget levels for a longer time frame compared to reefs with shallower
median depths [@fig-access-esm1-5-depth-carbonate]. Reef median depth has a moderate
positive correlation with the number of years a reef maintains coral cover above the
required threshold [@fig-access-esm1-5-depth-carbonate]. Depth - carbonate budget
maintainence correlation decreases as the required carbonate budget threshold increases.
This is likely due to an increasing number of reefs being unable to maintain coral cover
above threshold levels as the threshold increases, with values becoming increasingly
right-skewed. The natural log of total connectivity strength was found to have no 
correlation with the number of years a reef maintains cover above the required thresholds
[@sfig-access-esm1-5-conn-carbonate]. Log connectivity strength - carbonate budget 
maintainence correlation slightly decreases as the required carbonate budget threshold
increases.
